\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-12 journalSwarmControl/Introduction.tex
finished Becker edits to entire paper

 This paper is the synthesis of two preliminary conference papers,  \cite{swarmcontrol2013}, covered first few months of SwarmControl.net experiments, and \cite{ShahrokhiIROS2015}, presented simulations of object manipulation.  This paper presents the final results from SwarmControl.net.  All hardware validation experiments are new.

>>>>

 This paper is the synthesis of two preliminary conference papers.  \cite{swarmcontrol2013}, covered the first three months of SwarmControl.net experiments, and \cite{ShahrokhiIROS2015}, presented simulations of object manipulation.  This paper presents the final results from SwarmControl.net.  All hardware validation experiments are new.

### 2016-08-12 journalSwarmControl/expResults.tex
finished Becker edits to entire paper

Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. This experiment varied from 1 to 500 the population of robots used to transport an object. We kept the total area, maximum robot speed, and total net force the swarm could produce constant. The robots pushed a large hexagonal object through an  {\sffamily S}-shaped maze. Our hypothesis was that participants would complete the task faster with more robots. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minima around 130 robots.

\paragraph{Varying visualization}

Sensing is expensive, especially on the nanoscale. To see nanocars~\cite{Chiang2011} fastened molecules that fluoresce light when activated by a strong light source. Unfortunately, multiple exposures can destroy these molecules, a process called \emph{photobleaching}. Photobleaching can be minimized by lowering the excitation light intensity, but \cite{Cazes2001} showed this increases the probability of missed detections.  This experiment explores manipulation with varying amounts of sensing information: {\bf full-state} sensing provides the most information by showing the position of all robots; {\bf convex-hull} draws a convex hull around the outermost robots; {\bf mean} provides the average position of the population; and {\bf mean + variance} adds a confidence ellipse. Fig.~\ref{fig:Visualization} shows screenshots of the same robot swarm with each type of visual feedback. Full-state requires $2n$ data points for $n$ robots. Convex-hull requires at worst $2n$, but according to \cite{har2011expected}, the expected number is $O(2 n^{1/3})$.  Mean requires two, and variance three, data points.  Mean and mean + variance are convenient even with millions of robots. Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.24\columnwidth}
\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\put(20,15){Full-state}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisCH.pdf}\put(10,15){Convex-hull}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}\put(10,15){Mean + var}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMe.pdf}\put(30,15){Mean}\end{overpic}
\vspace{-.5em}
\caption{\label{fig:Visualization}Screenshots from task \emph{Vary Visualization}. This experiment challenges players to quickly steer 100 robots (blue discs) to push an object (green hexagon) into a goal region. We record the completion time and other statistics.
%\vspace{-1em}
}
\end{figure}

Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean + variance, mean, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers found convex-hull feedback confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

\paragraph{Varying noise}
Microrobots are affected by turbulence caused by random collisions with molecules. The effect of these collisions is called Brownian motion.

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryNoise.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{ResPositioning.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryNoisePosition} Left: Varying the noise from 0 to 200\% of the maximum control input resulted in only a small increase in completion time. Right: Increasing the number of robots resulted in longer completion times.  For more than 4 robots the goal pattern contained a void, which may have caused the longer completion times.
%\vspace{-1em}
}
\end{figure}

>>>>

Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. This experiment varied from 1 to 500 the population of robots used to transport an object. The total area, maximum robot speed, and total net force the swarm could produce were constant. The robots pushed a large hexagonal object through an  {\sffamily S}-shaped maze. We hypothesized participants would complete the task faster with more robots. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minima around 130 robots.

\paragraph{Varying visualization}
\begin{figure}[b!]
\renewcommand{\figwid}{0.24\columnwidth}
\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\put(20,15){Full-state}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisCH.pdf}\put(10,15){Convex-hull}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}\put(10,15){Mean + var}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMe.pdf}\put(30,15){Mean}\end{overpic}
\vspace{-.5em}
\caption{\label{fig:Visualization}Screenshots from task \emph{Vary Visualization}. This experiment challenges players to quickly steer 100 robots (blue discs) to push an object (green hexagon) into a goal region. We record the completion time and other statistics.
%\vspace{-1em}
}
\end{figure}

Sensing is expensive, especially on the nanoscale. To see nanocars~\cite{Chiang2011} fastened molecules that fluoresce light when activated by a strong light source. Unfortunately, multiple exposures can destroy these molecules, a process called \emph{photobleaching}. Photobleaching can be minimized by lowering the excitation light intensity, but \cite{Cazes2001} showed this increases the probability of missed detections.  This experiment explores manipulation with varying amounts of sensing information: {\bf full-state} sensing provides the most information by showing the position of all robots; {\bf convex-hull} draws a convex hull around the outermost robots; {\bf mean} provides the average position of the population; and {\bf mean + variance} adds a confidence ellipse. Fig.~\ref{fig:Visualization} shows screenshots of the same robot swarm with each type of visual feedback. Full-state requires $2n$ data points for $n$ robots. Convex-hull requires at worst $2n$, but according to \cite{har2011expected}, the expected number is $O(2 n^{1/3})$.  Mean requires two, and variance three, data points.  Mean and mean + variance are convenient even with millions of robots.

@@

Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.
Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [ mean, mean + variance, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers described convex-hull feedback as confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

\paragraph{Varying noise}
Microrobots are affected by random collisions with molecules. The effect of these collisions is called Brownian motion.

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryNoise.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{ResPositioning.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryNoisePosition} Left: Varying the noise from 0 to 200\% of the maximum control input resulted in only a small increase in completion time. Right: Increasing the number of robots resulted in longer completion times.  For more than 4 robots the goal pattern contained a void, which may have caused the jump in completion times.
%\vspace{-1em}
}
\end{figure}

### 2016-08-12 journalSwarmControl/experiment.tex
finished Becker edits to entire paper

This section analyzes an \emph{object manipulation} task attempted by both our hybrid, hysteresis-based controller, inspired by the analysis of human users in \S~\ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

 To avoid obstacles, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration,  as described in \cite{Thrun2005}, is used to learn an \emph{optimal policy}: a function that assigns a control input to every possible state.
 At each state the object can be commanded to move in one of eight directions with a small probability of moving in the wrong direction.

 A corresponding reward function gives a high reward to the goal state,  
 a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,\mathbf{u})$ is defined as
\begin{align}
r(x,u) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } \mathbf{u} \textrm{ leads to goal state}\\
      -100, & \textrm{if } \mathbf{u} \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
where $\mathbf{u}$ is the action and $x$ is the current state. 
  Value iteration iteratively learns the value $\hat{V}(x)$ for the object being in each state $x$. The optimal policy is the control action that, in probability, results in the largest value:
   \begin{align} \mathbf{D}(x) = \arg\max_{\mathbf{u}}   [ r(x,\mathbf{u}) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j| \mathbf{u},x)].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_{\mathbf{u}} [r(x_j,\mathbf{u}) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| \mathbf{u},x_j)] \label{eq:ValueIteration}\\
\text{end}& \nonumber
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \href{https://www.mathworks.com/matlabcentral/fileexchange/49992-mdp-robot-grid-world-example}{\emph{MDP grid world example}}.%\todo{link to algorithm}.  
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required a mean and standard deviation of $183\pm 179$ s while Policy Iteration required $90\pm 35$ s.
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

\begin{figure}
\centering
\begin{overpic}[scale=0.19]{GradientView.png}
\end{overpic}
\begin{overpic}[scale=0.19]{PolicyIter.png}
\end{overpic}
\begin{overpic}[scale=0.262]{MDPmap.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:BFSGradient}The BFS algorithm finds the shortest path for the moveable object  to compute gradient vectors (left). Modeling as an MDP enables encoding penalties for being near obstacles. (Middle) The control policy from value iteration. (Right) The vision algorithm detects obstacles, used to produce the
value function and control policy for the hardware setup. 
%\vspace{-2em}
}
\end{figure}

@@

Unfortunately, when the swarm is in front of the object, control law \eqref{eq:PDcontrolPosition} pushes the object backwards.  To fix this, we implement a potential field approach \cite{spong2008robot} that attracts the swarm to the intermediate goal, but repulses the swarm from in front of the object.
The repulsive potential field is centered at the object's COM and is active for a radius $\rho_0$, but is implemented only when the swarm mean is within $\theta$ of the desired direction of motion $\mathbf{D}(\mathbf{b})$ as shown in Fig.~\ref{fig:potentialField}.
\begin{align}
F_{att} &= -\zeta \Delta \rho / \rho \\
%\mathbf{u} &= [\bar{x},\bar{y}] - \mathbf{b} \nonumber \\
\phi &=\cos^{-1}\left( \frac{ \mathbf{D}(\mathbf{b}) \cdot ( [\bar{x},\bar{y}] - \mathbf{b}) }{\norm{\mathbf{D}(\mathbf{b})} \norm{ [\bar{x},\bar{y}] - \mathbf{b}} } \right) \\
%\theta &= \mathrm{angularDistance}\left( \alpha, \beta \right)\nonumber \\
 F_{rep} &=  \left\{
\begin{array}{ll}
      \eta( 1/\rho- 1/\rho_0) \frac{1}{\rho^2} \Delta \rho, ~& \rho\leq \rho_0~\&~\phi <  \theta \\
      0, & \textrm{ otherwise} \\
\end{array} 
\right.\\
F_{pot} &= F_{att} + F_{rep} \label{eq:potentialfield}
\end{align}

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. The controller in \cite{Shahrokhi2015} failed in $14\%$ trials, often because workspace obstacles made some robots unable to reach the object. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all robots in the workspace. Robots that cannot reach the object due to obstacles skew these calculations. The state machine in Fig.\ \ref{fig:Region}.a solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The main regions are generated by extending obstacles until they meet another obstacle shown in Fig.~\ref{fig:Region}.b. The transfer regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions shown in Fig.~\ref{fig:Region}.c.
This filtering increases experimental success because the mean calculation only includes nearby robots that can directly interact with the object. In the example, we want the robots to push the object to the right. Without filtering the robots, the orange star is the mean and the algorithm would instruct the robots to push the object southeast. The filtered mean is at the yellow star and the algorithm instructs the robots to push the object directly east. 
%When the object leaves main region 1 the maze state switches to transfer. 
%The object is in transfer region 0, so only robots in transfer region 0 are included in the mean and covariance calculations.  
%This heuristic improves performance by $50\%$ or less regarding the object heaviness.
In 10 simulations with 100 robots, completion time without outlier rejection required $\mu=245, \sigma=135$ s while using outlier rejection required $\mu=90, \sigma=35$ s.
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf}\end{overpic}
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}\end{overpic}\\
	\vspace{0.5em}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\end{overpic}
\end{center}
\caption{\label{fig:Region}  Outlier rejection state machine and regions.
}
\end{figure*}

@@

\begin{figure*}
\centering
%\renewcommand{\figwid}{0.19\columnwidth}
%\href{http://youtu.be/tCej-9e6-4o}{\begin{overpic}[width =\figwid]{story1.png}\put(6,15){T = 5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story2.png}\put(6,15){T = 12 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story3.png}\put(6,15){T = 20 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story4.png}\put(6,15){T = 25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story5.png}\put(6,15){T = 33 s}
%\end{overpic}}
\begin{overpic}[width =\columnwidth]{SwarmRun.pdf}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:story}\href{http://youtu.be/tCej-9e6-4o}{Snapshots showing an object manipulation simulation with 100 robots under automatic control.  See animation in~\cite{ShivaVideo2015}.}
%\vspace{-2em}
}
\end{figure*}

>>>>

This section analyzes an \emph{object manipulation} task attempted by both our hybrid, hysteresis-based controller, inspired by the analysis of human users in \S \ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

 To avoid obstacles, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration,  as described in \cite{Thrun2005}, is used to learn an \emph{optimal policy}: a function that assigns a control input to every possible state.
 At each state the object can be commanded to move in one of eight directions with a small probability of moving in a wrong direction.

 A corresponding reward function gives a high reward to the goal state,  
 a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,\mathbf{u})$ is defined as
\begin{align}
r(x,u) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } \mathbf{u} \textrm{ leads to goal state}\\
      -100, & \textrm{if } \mathbf{u} \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
 $\mathbf{u}$ is the action and $x$ is the current state. 
  Value iteration iteratively learns the value $\hat{V}(x)$ for the object being in each state $x$. The optimal policy is the control action that, in probability, results in the largest value:
   \begin{align} \mathbf{D}(x) = \arg\max_{\mathbf{u}}   [ r(x,\mathbf{u}) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j| \mathbf{u},x)].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_{\mathbf{u}} [r(x_j,\mathbf{u}) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| \mathbf{u},x_j)] \label{eq:ValueIteration}\\
\text{end}& \nonumber
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \cite{Becker2015MDP}.
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required $\mu=183$, $\sigma=179$ s while Policy Iteration required $\mu=90$, $\sigma=35$ s.
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

\begin{figure}
\centering
\begin{overpic}[scale=0.19]{GradientView.png}
\end{overpic}
\begin{overpic}[scale=0.19]{PolicyIter.png}
\end{overpic}
\begin{overpic}[scale=0.262]{MDPmap.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:BFSGradient}The BFS algorithm finds the shortest path for the moveable object  to compute gradient vectors (left). Modeling as an MDP enables encoding penalties for being near obstacles. (Middle) The control policy from value iteration. (Right) The vision algorithm detects obstacles in the hardware setup. This map is used to produce the value function and control policy shown. 
%\vspace{-2em}
}
\end{figure}

@@

Unfortunately, when the swarm is in front of the object, control law \eqref{eq:PDcontrolPosition} pushes the object backwards.  To fix this, we implement a potential field approach inspired by \cite{spong2008robot} that attracts the swarm to the intermediate goal, but repulses the swarm from in front of the object.
The repulsive potential field is centered at the object's COM and is active for a radius $\rho_0$, but is implemented only when the swarm mean is within $\theta$ of the desired direction of motion $\mathbf{D}(\mathbf{b})$ as shown in Fig.~\ref{fig:potentialField}.
\begin{align}
F_{att} &= -\zeta \Delta \rho / \rho \\
%\mathbf{u} &= [\bar{x},\bar{y}] - \mathbf{b} \nonumber \\
\phi &=\cos^{-1}\left( \frac{ \mathbf{D}(\mathbf{b}) \cdot ( [\bar{x},\bar{y}] - \mathbf{b}) }{\norm{\mathbf{D}(\mathbf{b})} \norm{ [\bar{x},\bar{y}] - \mathbf{b}} } \right) \\
%\theta &= \mathrm{angularDistance}\left( \alpha, \beta \right)\nonumber \\
 F_{rep} &=  \left\{
\begin{array}{ll}
      \eta( 1/\rho- 1/\rho_0) \frac{1}{\rho^2} \Delta \rho, ~& \rho\leq \rho_0~\&~\phi <  \theta \\
      0, & \textrm{ otherwise} \\
\end{array} 
\right.\\
F_{pot} &= F_{att} + F_{rep} \label{eq:potentialfield}
\end{align}

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. The controller in \cite{Shahrokhi2015} failed in $14\%$ trials, often because workspace obstacles made some robots unable to reach the object. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all robots in the workspace. Robots that cannot reach the object due to obstacles skew these calculations. The state machine in Fig.\ \ref{fig:Region} solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The main regions are generated by extending obstacles until they meet another obstacle. The transfer regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions.
This filtering increases experimental success because the mean calculation only includes nearby robots that can directly interact with the object. 
%In the example, we want the robots to push the object to the right. Without filtering the robots, the orange star is the mean and the algorithm would instruct the robots to push the object southeast. The filtered mean is at the yellow star and the algorithm instructs the robots to push the object directly east. 
%When the object leaves main region 1 the maze state switches to transfer. 
%The object is in transfer region 0, so only robots in transfer region 0 are included in the mean and covariance calculations.  
%This heuristic improves performance by $50\%$ or less regarding the object heaviness.
In 10 simulations with 100 robots, completion time without outlier rejection required $\mu=245, \sigma=135$ s while using outlier rejection required $\mu=90, \sigma=35$ s.
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\end{overpic}\\
	\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf}\end{overpic}
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}\end{overpic}
\end{center}
\vspace{-0.5em}
\caption{\label{fig:Region}  Outlier rejection state machine and regions.
}
\end{figure*}

@@

\begin{figure*}
\centering
%\renewcommand{\figwid}{0.19\columnwidth}
%\href{http://youtu.be/tCej-9e6-4o}{\begin{overpic}[width =\figwid]{story1.png}\put(6,15){T = 5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story2.png}\put(6,15){T = 12 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story3.png}\put(6,15){T = 20 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story4.png}\put(6,15){T = 25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story5.png}\put(6,15){T = 33 s}
%\end{overpic}}
\begin{overpic}[width =\columnwidth]{SwarmRun.pdf}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:story}\href{http://youtu.be/tCej-9e6-4o}{Snapshots showing an object manipulation simulation with 100 robots under automatic control.  See video in multimedia extension.}
%\vspace{-2em}
}
\end{figure*}

### 2016-08-12 journalSwarmControl/realExperiment.tex
finished Becker edits to entire paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Object manipulation with hardware robots}\label{sec:realExperiment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our experiments use centimeter-scale hardware systems called \emph{kilobots}.  While those are far larger than the micro scale devices we model, using kilobots allows us to emulate a variety of dynamics, while enabling a high degree of control over robot function, the environment, and data collection. The kilobot, reported in \cite{Rubenstein2012,rubenstein2014programmable}, is a low-cost robot designed for testing collective algorithms with large numbers of robots. It is available commercially or as an open source platform from \cite{K-Team2015}.  Each robot is approximately 3 cm in diameter, 3 cm tall, and uses two vibration motors to move on a flat surface at speeds up to 1 cm/s.  Each robot has one ambient light sensor that is used to implement \emph{phototaxis},  moving towards a light source.

\subsection{Environmental setup}  
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1.5 m$\times$1.2 m whiteboard as the workspace, and lights: four 50W LED floodlights  at the corners and four 30W LED floodlights on the sides of a 6 m square centered on the workspace and 1.5 m above the table. An Arduino Uno connected to an 8 relay shield controlled the lights.

Above the table, an overhead machine vision system tracks the swarm. The vision system identifies obstacles by color segmentation, determines the corners  (used to decrease  variance)  by topology, the object by color segmentation, and identifies robots using color segmentation and circle detection with a circular Hough transform.

The Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository,~\cite{Shahrokhi2015GitHubShapeControl}. 
The objects were 3D printed from ABS plastic with a paper overlay. 
Shapes included a 325 cm$^2$ equilateral triangle, 
%Small Equilateral Triangle 140 cm$^2$,
 324 cm$^2$ square,
 281 cm$^2$ hexagon,
254 cm$^2$ circle, 
and a 486 cm$^2$ (18 cm$\times$27 cm)  rectangle, all shown in Fig.~\ref{fig:setup}.

@@

Unlike the PD controller \eqref{eq:PDcontrolPosition}, we cannot command a force input to the kilobots.  Instead, control is given by turning on one of eight lights.  The kilobots run a phototaxis routine where they search for an orientation that aligns them with the light source, and then move with an approximately constant velocity toward this light.  In practice, because the kilobots only have one light detector, they oscillate along this orientation.

We use the sign of \eqref{eq:PDcontrolPosition}, and choose the closest orientation among the eight light sources.
Fig.~\ref{fig:realMean} shows that this limited, discretized control still enables regulating the mean position of a swarm of 100 robots.

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace. The same controller as in the simulation, Alg.~\ref{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}.  Trials were run until the object COM entered the goal region.  The trials ran for \{24:25, 57:37, 50:00, 36:02, 45:07\} minutes.  This is a mean of 42:38 and a standard deviation of 12:51 minutes. 
A circular object completed in 52:35 minutes. 
A square object completed in 114:31 minutes. 
A triangular object completed in XX:YY minutes.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=.9\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(49,8){\emph{t} = 2185 s}\put(83,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller classifies pink objects as obstacles and generates a policy to the goal. See the video attachment for an animation~\cite{ShivaVideo2015}}
%\vspace{-2em}
}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Object manipulation with hardware robots}\label{sec:realExperiment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our experiments use centimeter-scale hardware systems called \emph{kilobots}.  While those are far larger than the micro scale devices we model, using kilobots allows us to emulate a variety of dynamics, while enabling a high degree of control over robot function, the environment, and data collection. The kilobot, reported in \cite{Rubenstein2012,rubenstein2014programmable}, is a low-cost robot designed for testing collective algorithms with large numbers of robots. It is available as an open-source platform or commercially from \cite{K-Team2015}.  Each robot is approximately 3 cm in diameter, 3 cm tall, and uses two vibration motors to move on a flat surface at speeds up to 1 cm/s.  Each robot has one ambient light sensor that is used to implement \emph{phototaxis},  moving towards a light source.

\subsection{Environmental setup}  
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1.5 m$\times$1.2 m whiteboard as the workspace, and lights: four 50W LED floodlights  at the corners and four 30W LED floodlights on the sides of a 6 m square centered on the workspace and 1.5 m above the table. An Arduino Uno connected to an 8-relay shield controlled the lights.

Above the table, an overhead machine vision system tracks the swarm. The vision system identifies obstacles by color segmentation, determines the corners  (used to decrease  variance), the object by color segmentation, and identifies robots using color segmentation and circle detection with a circular Hough transform.

The laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository,~\cite{Shahrokhi2015GitHubShapeControl}. 
The objects were 3D printed from ABS plastic with a paper overlay. 
Shapes included a 325 cm$^2$ equilateral triangle, 
%Small Equilateral Triangle 140 cm$^2$,
 324 cm$^2$ square,
 281 cm$^2$ hexagon,
254 cm$^2$ circle, 
and a 486 cm$^2$ (18 cm$\times$27 cm)  rectangle, all shown in Fig.~\ref{fig:setup}.

@@

Unlike the PD controller \eqref{eq:PDcontrolPosition}, we cannot command a force input to the kilobots.  Instead, control is given by turning on one of eight lights.  The kilobots run a phototaxis routine where they search for an orientation that aligns them with the light source, and then move with an approximately constant velocity toward this light.   The kilobots oscillate along this orientation because they only have one light detector.

We use the sign of \eqref{eq:PDcontrolPosition}, and choose the closest orientation to $\mathbf{D}(\mathbf{b})$ among the eight light sources.
Fig.~\ref{fig:realMean} shows that this limited, discretized control still enables regulating the mean position of a swarm of 100 robots.

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace. The same controller as in the simulation, Alg.~\ref{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}, available at \todo{matlab link}.  
Trials were run until the object COM entered the goal region.  The trials ran for \{24:25, 57:37, 50:00, 36:02, 45:07\} minutes.  This is a mean of 42:38 and a standard deviation of 12:51 minutes. 
A circular object completed in 52:35 minutes. 
A square object completed in 114:31 minutes. 
A triangular object completed in XX:YY minutes.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=.9\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(49,8){\emph{t} = 2185 s}\put(83,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller classifies pink objects as obstacles and generates a policy to the goal. See  video in multimedia extension.}
%\vspace{-2em}
}
\end{figure}
